university ranking data

### 2022-06-02 inst/universities.Rmd
minor changes

---
title: "universities"
output: bookdown::html_document2
---

@@

## University ranking data

First load the data:

```{r cars}
universities_table <- read.table("universities.txt",header=TRUE)
head(universities_table,12)
```

>>>>

---
title: "university ranking data"
output: bookdown::html_document2
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

Here I analyse a dataset on NZ university rankings, taken from the
Times Higher Educational Supplement.  First load the data:

```{r loadthetable}
universities_table <- read.table("universities.txt",header=TRUE)
head(universities_table,12)
```
